---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

```{r}
setwd("C:/Users/Kanha/Desktop/Coursera/repdata_data_activity")

data<- read.csv("activity.csv")
data$date<- as.Date(data$date)

```

## What is mean total number of steps taken per day?

```{r}
stepsbyday<- tapply(data$steps, data$date, sum, na.rm=TRUE)
library(ggplot2)

qplot(stepsbyday, xlab="No. of Steps Taken Each Day", ylab="Total Frequency", binwidth=500)


medianbyday<- median(stepsbyday)
meanbyday<- mean(stepsbyday)

```

- Median = `r medianbyday`
- Mean = `r meanbyday`

## What is the average daily activity pattern?

```{r}
avg<- tapply(data$steps, data$interval, mean, na.rm=TRUE)

plot(names(avg), avg, xlab="5-min interval", type="l", ylab="Average no. of steps")



maxavg<- max(avg)
maxinterval<- as.numeric(names(avg)[which(avg==max(avg))])
```
- 5-minute interval : `r maxinterval`
- Max Average Value : `r maxavg`

## Imputing missing values

```{r}
totalna<- sum(is.na(data$steps))
```

- Total NAs : `r totalna`

```{r}
imputedata<- data


imputedata$steps[which(is.na(data$steps))]<- as.vector(avg[as.character(data[which(is.na(data$steps)),3])])


stepseachday<- tapply(imputedata$steps, imputedata$date, sum, na.rm=TRUE)

qplot(stepseachday, xlab="No. of Steps Taken Each Day", ylab="Total Frequency", binwidth=500)



medianEachDayImputed<- median(stepseachday)
meanEachDayImputed<- mean(stepseachday)
```

- Mean Total No. of Steps Taken Per Day : `r meanEachDayImputed`
- Median Total No. of Steps Taken Per Day : `r meanEachDayImputed`

## Are there differences in activity patterns between weekdays and weekends?

```{r}
imputedata$dayType<- ifelse(as.POSIXlt(imputedata$date)$wday %in% c(0,6), "weekends","weekdays")


aggregateData<- aggregate(steps ~ interval + dayType, data=imputedata, mean)

ggplot(aggregateData, aes(interval, steps)) + 
  geom_line() + 
  facet_grid(dayType ~ .) +
  xlab("5-minute interval") + 
  ylab("avarage number of steps")

```
